### 2023-01-27 article.tex
T test example is genetic epidemiological

To illustrate how easy it is to get a mismatch between a paper
and the code, consider this example
of a text in a fictional paper:

\begin{verbatim}
We compared the values of x and y using an unpaired one-tailed Student's T-test,
as we expect the average value of x to be less than the average value of y.
\end{verbatim}

@@

\begin{verbatim}
t.test(x, y)
\end{verbatim}

@@

To approach the same problem from a different angle:
correctly reporting the T-test in a reproducable ways
is already a problem, with only 80 out of a selected 179 papers
fully reporting the parity of T-test (i.e. paired or unpaired) 
\cite{weissgerber2018we}.
In those unresolved 99 papers, 
the code (if published) would clarify this.

>>>>

To illustrate how easy it is to get a mismatch between a paper
and the code, 
consider this example of a possible text in the fictional 
genetic epidemiology paper:

\begin{verbatim}
We compared the in-blood concentrations of IL6RA 
between subjects having AA versus subjects having GG at SNP rs12133641,
using an unpaired one-tailed T-test,
as we expect the average concentration of IL6RA for those with AA 
to be less than the average concentration in those with GG.
\end{verbatim}

@@

\begin{verbatim}
t.test(subjects_with_aa, subjects_with_gg)
\end{verbatim}

@@

Note that there is another side of this same coin:
correctly reporting the T-test in a reproducable ways
is known to be a problem, with only 80 out of a selected 179 papers
fully reporting the parity of T-test (i.e. paired or unpaired) 
\cite{weissgerber2018we}.
In those unresolved 99 papers, 
the code (if published) would clarify this.
